Using Refactoring Techniques to Reduce Duplication in Object-Oriented Programming Languages\\- Work in Progress -

### 2019-04-24 sattose/paper.tex
Better formatting and such

@@

\begin{table}[H]
\begin{tabular}{|l|l|l|} \hline
\textbf{Relation}  & \textbf{Amount} & \textbf{Percentage} \\ \hline
Unrelated          & 13537           & 39,39               \\ \hline
Same Class          & 8341            & 24,27               \\ \hline
Sibling            & 5978            & 17,39               \\ \hline
Same Method         & 2456            & 7,15                \\ \hline
External Superclass & 2402            & 6,99                \\ \hline
First Cousin        & 695             & 2,02                \\ \hline
Superclass         & 488             & 1,42                \\ \hline
Common Hierarchy    & 442             & 1,29                \\ \hline
Ancestor           & 28              & 0,08               \\ \hline
\end{tabular}
\end{table}

@@

\begin{table}[H]
\begin{tabular}{|l|l|l|}
\hline
\textbf{Location} & \textbf{Amount} & \textbf{Percentage} \\ \hline
Method Level       & 19817           & 57,66               \\ \hline
Class Level        & 14366           & 41,80               \\ \hline
Interface Level    & 110             & 0,32                \\ \hline
Enum Level         & 74              & 0,22                \\ \hline
\end{tabular}
\end{table}
%TODO: Add and discuss measurements

@@

%TODO: Finish text and add measurements.

@@

\begin{table}[H]
\begin{tabular}{|l|l|l|}
\hline
\textbf{Contents}       & \textbf{Amount} & \textbf{Percentage} \\ \hline
HASINTERFACEDECLARATION & 10              & 0,03                \\ \hline
SEVERALMETHODS          & 9077            & 26,41               \\ \hline
FULLCLASS               & 198             & 0,58                \\ \hline
FULLENUM                & 4               & 0,01                \\ \hline
FULLMETHOD              & 554             & 1,61                \\ \hline
INCLUDESFIELDS          & 1150            & 3,35                \\ \hline
HASCLASSDECLARATION     & 445             & 1,29                \\ \hline
HASENUMDECLARATION      & 47              & 0,14                \\ \hline
FULLINTERFACE           & 6               & 0,02                \\ \hline
HASENUMFIELDS           & 52              & 0,15                \\ \hline
PARTIALMETHOD           & 19263           & 56,05               \\ \hline
ONLYFIELDS              & 565             & 1,64                \\ \hline
OTHER                   & 2996            & 8,72                \\ \hline
\end{tabular}
\end{table}
%TODO: Show measurements

>>>>

Running our clone detection script, CloneRefactor, over this corpus gives the following results:

@@

\begin{table}[H]
\begin{tabular}{|l|l|l|} \hline
\textbf{Relation}  & \textbf{Amount} & \textbf{Percentage} \\ \hline
Unrelated          & 13.537           & 39,39               \\ \hline
Same Class          & 8.341            & 24,27               \\ \hline
Sibling            & 5.978            & 17,39               \\ \hline
Same Method         & 2.456            & 7,15                \\ \hline
External Superclass & 2.402            & 6,99                \\ \hline
First Cousin        & 695             & 2,02                \\ \hline
Superclass         & 488             & 1,42                \\ \hline
Common Hierarchy    & 442             & 1,29                \\ \hline
Ancestor           & 28              & 0,08               \\ \hline
\end{tabular}
\end{table}

@@

\begin{table}[H]
\begin{tabular}{|l|l|l|}
\hline
\textbf{Location} & \textbf{Amount} & \textbf{Percentage} \\ \hline
Method Level       & 19.817           & 57,66               \\ \hline
Class Level        & 14.366           & 41,80               \\ \hline
Interface Level    & 110             & 0,32                \\ \hline
Enum Level         & 74              & 0,22                \\ \hline
\end{tabular}
\end{table}

From these results we can see, somewhat surprisingly, that in our

@@

\begin{table}[H]
\begin{tabular}{|l|l|l|}
\hline
\textbf{Contents}       & \textbf{Amount} & \textbf{Percentage} \\ \hline
HASINTERFACEDECLARATION & 10              & 0,03                \\ \hline
SEVERALMETHODS          & 9.077            & 26,41               \\ \hline
FULLCLASS               & 198             & 0,58                \\ \hline
FULLENUM                & 4               & 0,01                \\ \hline
FULLMETHOD              & 554             & 1,61                \\ \hline
INCLUDESFIELDS          & 1.150            & 3,35                \\ \hline
HASCLASSDECLARATION     & 445             & 1,29                \\ \hline
HASENUMDECLARATION      & 47              & 0,14                \\ \hline
FULLINTERFACE           & 6               & 0,02                \\ \hline
HASENUMFIELDS           & 52              & 0,15                \\ \hline
PARTIALMETHOD           & 19.263           & 56,05               \\ \hline
ONLYFIELDS              & 565             & 1,64                \\ \hline
OTHER                   & 2.996            & 8,72                \\ \hline
\end{tabular}
\end{table}
%TODO: Finish text and add measurements.

@@

%TODO: Show measurements
